Emergent dual scaling of riverine biodiversity

### 2021-06-30 manuscript_pnas.Rmd
edits: manuscript

The past two decades have witnessed efforts to illuminate the role of spatial ecosystem structure in shaping biodiversity patterns [@rinaldoRiverNetworksEcological2018; @grantLivingBranchesPopulation2007]. Yet, current schemes have overlooked one of the fundamental rules in branching ecosystems, i.e., the dual scaling law. Our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings. This discovery, therefore, should bring a paradigm shift in macroecological science.

@@

Third parties provided data for empirical data analysis; references are provided where appropriate. R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>). Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_stream-diversity>.

>>>>

The past two decades have witnessed efforts to illuminate the role of spatial ecosystem structure in shaping biodiversity patterns [@rinaldoRiverNetworksEcological2018; @grantLivingBranchesPopulation2007]. Yet, current schemes have overlooked one of the fundamental phenomena in spatially complex ecosystems - the dual scaling law. Our unified framework unveiled the surprising consistency of dual scaling across ecological contexts or geographic regions, suggesting the universality of our findings. This discovery, therefore, should bring a crucial perspective to macroecological science.

@@

Part of our fish data set is available from the RiverFishTIME database [@comteRivFishTIMEGlobalDatabase2021]. The fish data provided by third parties are not available due to licensing issues. Environmental data are available at MERIT Hydro ([http://hydro.iis.u-tokyo.ac.jp/\\\~yamadai/MERIT_Hydro/](http://hydro.iis.u-tokyo.ac.jp/~yamadai/MERIT_Hydro/){.uri}) [@yamazakiMERITHydroHighResolution2019], Global 3-second/1-second Water Body Map ([http://hydro.iis.u-tokyo.ac.jp/\\\~yamadai/G3WBM/index.html](http://hydro.iis.u-tokyo.ac.jp/~yamadai/G3WBM/index.html){.uri}) [@yamazakiDevelopmentGlobal90m2015],WorldClim (<https://www.worldclim.org/data/v1.4/worldclim14.html>) [@hijmansVeryHighResolution2005], Copernicus Global Land Service (<https:/doi.org/10.5281/zenodo.3939038>) [@marcelbuchhornCopernicusGlobalLand2020], and Global Reservoir and Dam database (<https://doi.org/10.7927/H4N877QK>) [@lehnerGlobalReservoirDam2011]. R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>). Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_stream-diversity>.
